On g~0~

### 2017-03-27 manuscript.Rmd
more references and new outline

```{r echo=FALSE}
includefigs <- TRUE
library(png)
library(grid)

@@

@@

@@

@@

@@

@@

>>>>

```{r echo=FALSE}
includefigs <- F
library(png)
library(grid)

@@

# new outline

1. Introduction (short): questions about g0.
2. Need for inclusion of g0 in models
3. Comparison of values for various possible definitions
4. Estimation of g~0~ by fitting 
5. Nighttime conductance (v. short)
6. Cuticular conductance (short)
7. Minimum conductance (longer)
8. Recommendations and future work

@@

g~0~ is often defined as g~s~ when A approaches zero when PPFD approaches zero [@leuning1995] but it is clear from Eq. 1 that g~0~ is also attained when A approaches zero due to other environmental drivers, in particular temperature, and drought stress (which may either reduce photosynthetic capacity or g~1~, or both, see Zhou). It is not clear nor obvious whether these various minima should equal each other.

One estimate of g~0~ (low PPFD) comes from night-time measurements of conductance, which have been known for a long time to be substantially larger than zero. It is however not clear whether daytime g~0~ at low PPFD, for darkened leaves, is comparable in magnitude to g~0~ in the dark at night. Evidence from experiments where environmental conditions are held constant suggests that g~s~ varies tremendously throughout the day independent of these drivers, and has therefore been attributed to an internal clock (Resco).

@@

Implemented in the *plantecophys* R package [@duursma2015]

@@

@leuning1995 says "g0 > 0, otherwise ci/ca would be constant for all values of Q. The rate of convergence of ci to ca at low A (low Q) depends on the value of g0; when g0 is large, ci deviates from the asymptotic value at higher values of A than when g0 is small".

@@

"We have assumed in the following equations that when stomata are closed the leaf conductance is zero because field data are generally inadequate to define a cuticular conductance." [@jarvis1976]

The difficulty of this can be seen from the fact that a) many studies set g0 to something rather than fitting it (e.g. @leuning1995 uses 0.01 for all); presumably because unreliable estimates were obtained, b) negative fitted values are common [@leuning1995; @herault2013; @miner2016].

@@

g~0~ fitted is higher than minimum g~s~ from datasets. If we restric the fittings to those were g~0~ had a relatively narrow width of the confidence interval (< 0.03 mol m-2 s-1), then the average was `r with(subset(lin2015coef, g0_uci - g0_lci < 0.03), mean(g0))` compared to `r mean(lin2015coef$g0)` for all.
